### 2023-03-04 manuscript.tex
Update manubot.yaml [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ec905395a96fdfb763884c88fe68815dba1be09d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/ec905395a96fdfb763884c88fe68815dba1be09d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333050954

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c300807d221901c7441dc86e15a3e2c6c4d2f7c4/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c300807d221901c7441dc86e15a3e2c6c4d2f7c4}{SORTEE-Github-Hackathon/manuscript@c300807}
on 2023-03-04.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ec905395a96fdfb763884c88fe68815dba1be09d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ec905395a96fdfb763884c88fe68815dba1be09d}{SORTEE-Github-Hackathon/manuscript@ec90539}
on 2023-03-04.
